### 2021-05-26 geography/ia/paper.tex
typo fix
analysis & data start (work on this later pls)

\begin{figure}[H]
    \begin{minipage}{\textwidth}
        \centering
        \includegraphics[width=0.7\linewidth]{media/7esites.png}
        \caption{Map of sites chosen for the residential area, the XVI\textsuperscript{th} \textit{arrondissement}. Map base layer courtesy of Google Maps, pictures seen are taken on a mobile phone.}
    \end{minipage}
\end{figure}

@@

\section{Analysis}
\label{sec:analysis}

\textit{Not done}

\subsection{Environmental and cultural sustainability}
\textit{Not done}

\subsection{Economic sustainability}
\textit{Not done}

@@

\textit{Not done}

>>>>

\begin{figure}[H]
    \begin{minipage}{\textwidth}
        \centering
        \includegraphics[width=0.7\linewidth]{media/7esites.png}
        \caption{Map of sites chosen for the touristic area, the VII\textsuperscript{th} \textit{arrondissement}. Map base layer courtesy of Google Maps, pictures seen are taken on a mobile phone.}
    \end{minipage}
\end{figure}

@@

\section{Data \& Analysis}
\label{sec:analysis}

Once our data collected, we can analyse certain patterns that appear

\subsection{Data collected}

\subsection{Analysis}

@@

\subsection{Evaluation}

There are some processes in our paper that would be done differently if done now. For example:

\begin{itemize}

    \item The computer program does not seem to take into account an area of greenery in the VII\textsuperscript{th}, which can change the NNI value found for the VII\textsuperscript{th}. This area includes parks and such, however the map (generated also with the computer program) does not show trees in this location. This should have been investigated, however due to constraints related to time, I could not. 
    \item

\end{itemize}
